Verifying Demonstrations

### 2020-03-10 paper/DB-Schnorr-UWB.tex
Fixes UWB KE MITM problem: ties DH exponent to secret key
No proofs though.

In summary, the difference is as follows.
\(\DBS\) has a static shared key~\(k\) and performs \(
  \PK[\alpha][A = g^\alpha]
\) with a distance bound.
\(\DBSHW\) first runs \iac{DHKE} to establish the shared key~\(k =
\gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
performs \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ],
\] also with a distance bound; where \(\sk_P\) is the prover's private key, 
\(\sigma\) is a signature issued with signing key~\(\sk\) and \(\Blind\) 
reblinds a signature.
Proving knowledge of \(\xDH\) prevents any \ac{MITM} attack against the 
\ac{DHKE}.
Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
key~\(\sk_P\) ensures that the prover is a device in the \ac{PKI} of the 
\ac{CA}.

@@

    \(\xDH\rgets \ZZ_{\qDH}\)
    & \(\ProtoSendRight{\XDH = \gDH^{\xDH}}\)
    & \(\yDH\rgets \ZZ_{\qDH}\)
    \\

@@

    \(R\gets g^{\rho},
      \RDH\gets \gDH^{\rhoDH},
      \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}\)
    & \(\ProtoSendRight{R, \RDH, \RCL}\)
    &
    \\

@@

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
    \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\) (except in the 
    pre-setup phase).
    The protocol actually proves \(
      \PK[\alpha, \xDH, \sk, \sigma][
        A = g^\alpha \land
        \XDH = \gDH^{\xDH} \land
        \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
      ].
    \)
    This is ties \(\xDH\), and consequently \(k\), to \(\sk_P\) and \(\alpha\).
    The protocol (setup, distance-bounding and verification phases) should be 
    repeated \(n\) times to achieve the desired soundness and distance-bounding 
    errors.
  }%
  \label{DBSHW-overview}
\end{figure*}

@@

To establish \(k\), we use the \ac{DHKE}.
The prover chooses \(\xDH \rgets \ZZ_{\qDH}\), the verifier chooses 
\(\yDH\rgets \ZZ_{\qDH}\) and they exchange \(\XDH = \gDH^{\xDH}, \YDH = 
\gDH^{\yDH}\) and both compute
\(k = \gDH^{\xDH \yDH}\), for some generator \(\gDH\) in \iac{DH} group of 
prime order \(\qDH\).

@@

The prover chooses \[
  \rho\rgets \ZZ_q, \quad
  \rhoDH\rgets \ZZ_{\qDH}, \quad
  \rhoCL_{\sk}\rgets \ZZ_{\qCL}, \quad
  \rhoCL_r\rgets \ZZ_{\qCL}, \quad
  \rhoCL_{r'}\rgets \ZZ_{\qCL}
\] computes \[
  R\gets g^\rho, \quad
  \RDH\gets \gDH^{\rhoDH}, \quad
  \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}
\] and sends \(R, \RDH, \RCL\) to the verifier.

@@

The verifier checks that \[
  R = A^{c_i} g^{s_i}, \quad
  \RDH = \XDH^{c_i} g^{\sDH_i}, \quad
  v_x^{c_i} \RCL = v_s^{s_{r'}} v_{xy}^{s_{\sk_P}} V_{xy}^{s_r}
\] and that the round-trip time \(\Delta t < t_{\max}\) does not exceed the 
time-limit~\(t_{\max}\) (corresponding to the desired distance bound).
Finally, the verifier checks the validity of \(\tilde \sigma\): \[
  e(\tilde a, \ZCL) = e(\gCL, \tilde A), \quad
  e(\tilde a, \YCL) = e(\gCL, \tilde b), \quad
  e(\tilde A, \YCL) = e(\gCL, \tilde B).
\]

>>>>

In summary, the difference is as follows.
\(\DBS\) has a static shared key~\(k\) and performs \(
  \PK[\alpha][A = g^\alpha]
\) with a distance bound.
\(\DBSHW\) first runs \iac{DHKE} to establish the shared key~\(k =
\gDH^{\xDH \yDH}\) from \(\XDH = \gDH^{\xDH}, \YDH = \gDH^{\yDH}\), then 
performs \[
  \PK[\alpha, \xDH, \sk_P, \sigma][
    A = g^\alpha \land
    \XDH = \gDH^{\xDH} \land
    \XDHCL = \XDH^{\sk} \land
    \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
  ],
\] also with a distance bound; where \(\sk_P\) is the prover's private key, 
\(\sigma\) is a signature issued with signing key~\(\sk\) and \(\Blind\) 
reblinds a signature.
Proving knowledge of \(\XDH = \gDH^{\xDH}\) and \(\XDHCL = \XDH^{\sk}\) 
prevents any \ac{MITM} attack against the \ac{DHKE}.
Proving knowledge of a signature~\(\sigma\) by \iac{CA} on the private 
key~\(\sk_P\) ensures that the prover is a device in the \ac{PKI} of the 
\ac{CA}.

@@

    \(\xDH\rgets \ZZ_{\qDH}, \XDH\gets \gDH^{\xDH}, \XDHCL\gets \XDH^{\sk}\)
    & \(\ProtoSendRight{\XDH, \XDHCL}\)
    & \(\yDH\rgets \ZZ_{\qDH}\)
    \\

@@

    \(R\gets g^{\rho},
      \RDH\gets \gDH^{\rhoDH},
      \RDHCL\gets \XDH^{\rhoCL_{\sk}},
      \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}\)
    & \(\ProtoSendRight{R, \RDH, \RDHCL, \RCL}\)
    &
    \\

@@

    % null
    &
    & \(\RDHCL = \XDHCL^{c_i} \XDH^{\sCL_i^{(\sk)}}\),
    \\

@@

  \end{tabular}
  \caption{%
    One-round protocol instance of the \(\DBSHW\) protocol instantiating 
    \(\PK[\alpha][A = g^\alpha]\).
    Each transmission (arrow in the diagram) uses \(\UWBPR\) (except in the 
    pre-setup phase).
    The protocol actually proves \(
      \PK[\alpha, \xDH, \sk, \sigma][
        A = g^\alpha \land
        \XDH = \gDH^{\xDH} \land
        \XDHCL = \XDH^{\sk} \land
        \Blind[\sigma] = \Sign[_{\sk}][\sk_P]
      ].
    \)
    This is ties \(\xDH\), and consequently \(k\), to \(\sk_P\) and \(\alpha\).
    The protocol (setup, distance-bounding and verification phases) should be 
    repeated \(n\) times to achieve the desired soundness and distance-bounding 
    errors.
  }%
  \label{DBSHW-overview}
\end{figure*}

@@

To establish \(k\), we use the \ac{DHKE}.
The prover chooses \(\xDH \rgets \ZZ_{\qDH}\), the verifier chooses 
\(\yDH\rgets \ZZ_{\qDH}\) and they exchange \(\XDH = \gDH^{\xDH}, \YDH = 
\gDH^{\yDH}\) and both compute
\(k = \gDH^{\xDH \yDH}\), for some generator \(\gDH\) in \iac{DH} group of 
prime order \(\qDH\).
The prover also computes \(\XDHCL\rgets \XDH^{\sk}\) and sends to the verifier.

@@

The prover chooses \[
  \rho\rgets \ZZ_q, \quad
  \rhoDH\rgets \ZZ_{\qDH}, \quad
  \rhoCL_{\sk}\rgets \ZZ_{\qCL}, \quad
  \rhoCL_r\rgets \ZZ_{\qCL}, \quad
  \rhoCL_{r'}\rgets \ZZ_{\qCL}
\] computes \[
  R\gets g^\rho, \quad
  \RDH\gets \gDH^{\rhoDH}, \quad
  \RDHCL\gets \XDH^{\rhoCL_{\sk}}, \quad
  \RCL\gets v_s^{\rhoCL_{r'}} v_{xy}^{\rhoCL_{\sk}} V_{xy}^{\rhoCL_r}
\] and sends \(R, \RDH, \RCL\) to the verifier.

@@

The verifier checks that \[
  R = A^{c_i} g^{s_i}, \quad
  \RDH = \XDH^{c_i} g^{\sDH_i}, \quad
  \RDHCL = \XDHCL^{c_i} \XDH^{\sCL_i^{(\sk)}}, \quad
  v_x^{c_i} \RCL = v_s^{s_{r'}} v_{xy}^{s_{\sk_P}} V_{xy}^{s_r}
\] and that the round-trip time \(\Delta t < t_{\max}\) does not exceed the 
time-limit~\(t_{\max}\) (corresponding to the desired distance bound).
Finally, the verifier checks the validity of \(\tilde \sigma\): \[
  e(\tilde a, \ZCL) = e(\gCL, \tilde A), \quad
  e(\tilde a, \YCL) = e(\gCL, \tilde b), \quad
  e(\tilde A, \YCL) = e(\gCL, \tilde B).
\]

\subsection{Security analysis}

There are two questions we must answer about this protocol:
\begin{enumerate}
  \item Can the adversary perform \iac{MITM} attack against the \ac{DHKE}?
  \item Does \(\XDHCL\) break anonymity?
\end{enumerate}
